An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-03 paper/4.xpg.tex
small change

\noindent Now, let us see how we construct $pg$ recursively.

@@

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be undefined although there is no undefined when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively obvious.

>>>>

\noindent Now, let us see how we construct $pg$ respectively.

@@

The first equality is simply based on the definitions of $pg$, $\putbxinline{Skip \ h}$ and $\getbxinline{Skip \ h}$. The second one tuples two results of $put$ and $get$ in the body of the if-expression. This is a trick since in some cases, the result of $pg$ may be undefined although the result is not 
\end
undefined when evaluating $\getbxinline{Skip \ h}$. The last equality is relatively obvious.
